Enhancing Adversarial Robustness for Deep Metric Learning

### 2022-03-09 tex/robdml.tex
move everything under tex/
tex: add macro and switch to camera ready

@@

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
%\usepackage[review]{cvpr}      % To produce the REVIEW version
%\usepackage{cvpr}              % To produce the CAMERA-READY version
\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

@@

\author{Mo Zhou\\
Johns Hopkins University\\
{\tt\small mzhou32@jhu.edu}
\and
Vishal Patel\\
Johns Hopkins University\\
{\tt\small vpatel36@jhu.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle

@@

Further analysis, technical details, and limitations, \etc,
are presented in the supplementary document.

@@

%\textbf{Acknowledgements.} This research was supported by []. We thank
%Kangfu Mei for helpful discussions and feedbacks.

@@

\input{appendix.tex}

>>>>

% Copyright (C) 2021-2022 Mo Zhou <cdluminate@gmail.com>
% License: CC-BY-NC-SA-4.0
% Preprint: https://arxiv.org/abs/2203.01439
% Preprint License: CC-BY-NC-SA-4.0

@@

\documentclass[10pt,twocolumn,letterpaper]{article}
\newif\ifarxiv

%\arxivtrue % XXX
\arxivfalse % XXX

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
%\usepackage[review]{cvpr}      % To produce the REVIEW version
\ifarxiv
\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version
\else
\usepackage{cvpr}              % To produce the CAMERA-READY version
\fi

@@

\author{Mo Zhou\\
Johns Hopkins University\\
{\tt\small mzhou32@jhu.edu}
\and
Vishal M. Patel\\
Johns Hopkins University\\
{\tt\small vpatel36@jhu.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle

@@

\ifarxiv
Further analysis, technical details, and limitations, \etc,
are presented in the supplementary document.
\else
\fi

@@

\ifarxiv
\else
{\scriptsize
\textbf{Acknowledgements.} This work was supported by the DARPA GARD Program
HR001119S0026-GARD-FP-052. We thank Kangfu Mei for helpful feedbacks.
}
\fi

@@

\ifarxiv
\input{appendix.tex}
\else
\fi
